Verifying Demonstrations

### 2018-11-30 paper/privacy-analysis.tex
Fixes typo
moves timestamp uniquness problem/solution from analysis to building block

We start with \cref{ProtestUnlink}, that Alice's proofs must be unlinkable across protests but linkable within one protest due to \cref{CountOnce}.
It follows from the properties of \(\ACprf\) that \(\pid =  \ACprf[_{\sk_P}][\cid]\) and \(\pid' = \ACprf[_{\sk_P}][\cid']\) are unlinkable if \(\cid\neq \cid'\).

Afterwards to get the property \cref{ProofUnlink}.
Given \(\pid\), Grace cannot distinguish whether \(\pid = \ACprf[_{\sk_A}][\cid]\), \(\pid = \ACprf[_{\sk_A}][\cid']\) or \(\pid = \ACprf[_{\sk_B}][\cid]\) due to the properties of \(\AC\).

However, consider the situation in which the witness works for Grace.
This witness interacts with Alice directly and might have (physically) identified her.
The witness also learns Alice's \(\pid\), but not \(\cid\), to compute \(\wid\) and to verify the \ac{PPK}.
\daniel{This assumes that I will do the changes to hide \(\cid\) from the witness in the \ac{PPK}.}
Afterwards, Alice publishes \(\pid\) and \(\cid\) together as part of the proof 
share.
The probability of a colliding \(\pid = \ACprf[_\sk][\cid']\) for some \(\cid' 
  \neq \cid\) and \(\sk \neq \sk_P\) is \enquote{small}.
\daniel{Fix this.}
If this occurs, Grace could link \(\cid\) (and thus the opinions in the manifesto) to Alice.

\sonja{anonymity and cause unlinkability missing}

>>>>

We start with \cref{PseudonymUnlink}.
Given \(\pid\), \cref{in-system-adversary} cannot distinguish whether \(\pid = 
  \ACprf[_{\sk_A}][\cid]\) or \(\pid = \ACprf[_{\sk_B}][\cid]\) due to the 
properties of \(\AC\) (see~\cite{HowToWinTheCloneWars}).
This is not necessarily true for \cref{deanonymizing-storage-adversary}:
if everyone uploads their own proof shares\footnote{%
  This is probable due to the proof-of-correctness, \(\corr_\pid\), which is 
  likely computed after the protest has ended.
}, \cref{deanonymizing-storage-adversary} will link \(P\) and \(\pid\), and 
consequently \(P\) and \(\cid\).

\Cref{ProtestUnlink}, Alice's proofs must be unlinkable across protests.
This also follows from the properties of 
\(\ACprf\)~\cite{HowToWinTheCloneWars}: \(\pid =  \ACprf[_{\sk}][\cid]\) and 
\(\pid' = \ACprf[_{\sk}][\cid']\) (where \(\cid \neq \cid'\)) are unlinkable 
from the perspective of \cref{in-system-adversary}.
This is not true for \cref{deanonymizing-storage-adversary}: since 
\cref{deanonymizing-storage-adversary} can link \(\pid, P\) and \(\pid', P\); 
then \cref{deanonymizing-storage-adversary} can link \(\pid, \pid'\) too, thus 
violating \cref{ProtestUnlink}.
In the same way, \cref{deanonymizing-storage-adversary} can violate 
\cref{WitnessUnlink}.

However, the statement about \cref{ProtestUnlink,in-system-adversary} is not 
necessarily true for \cref{WitnessUnlink,in-system-adversary}.
The proof shares consist of more than only \(\cid, \pid, \wid\); more 
specifically, each proof share is a tuple \((\cid, \pid, \wid, t_s, t_s', l, 
  \corr_\pid, \corr_\wid)\).
Let \(\cid\) be fixed, then \(\pid\) is a unique identifier for \(P\).

We assume that the location \(l\) is coarse enough so that many non-overlapping 
\((\pid, \wid)\)-pairs use the same location.
Thus \(l\) is not unique for any individual (protester or witness).
This implies some degree of \(k\)-anonymity for the location \(l\).

Likewise, thanks to the constraints in the time-stamp granularity,
\(t\) is not unique.

### 2018-11-30 paper/timestamp.tex
moves timestamp uniquness problem/solution from analysis to building block

We need a robust time-stamping service, \(\TS\), which implements the \(\TSget\), \(\TSstamp\) and \(\TStime\) requests such that
\simon{"request" feels weird to me. Are we sure that's the right word?}
\begin{itemize}
  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that \(\TSverify[x, \pi]\to \top\) and \(\TStime[\pi] = t\).
\end{itemize}

@@

The tuple \((\rho_{t_0}, m, \pi_{t_1})\) can be used to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether \(\TSverify[h', \pi_{t_1}] = \top \land \TStime[\rho_{t_0}] > t_0\land 
  \TStime[\pi_{t_1}] < t_1\).

@@

>>>>

We need a robust time-stamping service, \(\TS\), which implements the \(\TSget\), \(\TSstamp\) and \(\TStime\) requests such that
\simon{"request" feels weird to me. Are we sure that's the right word?}
\begin{itemize}
  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that \(\TSverify[x, \pi]\to \top\) and \(\TStime[\pi] = t\).
\item the time stamp is chosen at a low enough rate to not be unique, \eg by using only every \(n\)th block from the underlying ledger.
\end{itemize}

@@

The tuple \((\rho_{t_0}, m, \pi_{t_1})\) can be used to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether 
\(\TSverify[h', \pi_{t_1}] = \top\) and \(\TStime[\rho_{t_0}] \geq t_0\land 
  \TStime[\pi_{t_1}] \leq t_1\).

@@

% Since \(\pid\) uniquely identifies \(P\), then if \(t_s^{(\pid)}\) is 
% \enquote{unique enough}\footnote{%
%   This can be verified thanks to \cref{CountOnce}.
%   If there are no tuples \((\pid, t_s)\) and \((\pid, t_s')\) among the proof 
%   shares such that \(\pid \neq \pid'\) but \(t_s = t_s'\), then \(t_s\) also 
%   \emph{likely} uniquely identifies \(P\).
%   \enquote{Likely} depends on the likelihood of there being witnesses who are 
%   not protesters.
% }, every \(\wid\) for which \(t_s' = t_s^{(\pid)}\) is \emph{likely} to be 
% \(P\) acting as a witness.
% This would allow \cref{in-system-adversary} to link \(\wid, \wid'\) for 
% different protesters, thus violating \cref{WitnessUnlink}.
% (The same can be said of \(\pid\) and \cref{ProtestUnlink} if there are 
% multiple protests, \ie \(\cid\)'s, at the same time and location.
% However, we deem this as unlikely.)

% Distribution of \(t_s\) depends on the rate of \(\TSget\) and the distribution 
% of when participants run the algorithm the last time.
% For example, if we use a six-hour interval and a rate of one new value per 
% minute, then there are potentially 21600 unique values for \(t_s\).
% However, we can scale this down by a factor \(n\) by requiring \(\TSget\) to 
% use only every \(n\)th block from the underlying ledger.
% Thus it seems reasonable that \(t_s\) will never be \enquote{unique enough}.
